Wireless service accounting based on Ethereum state channels - Master Thesis

### 2019-10-12 Paper.tex
Start automated tests description

\subsubsection{etherdoor}

@@

To validate the PoC, a battery of tests has been defined. For example, given
that smart contract normally handle money, it is essential to ensure that
its number of failures and vulnerabilities is low [Hegedus 18].
To help developers and make technology more mature,
we need analysis tools [ConsenSys 19].

@@

>>>>

\subsubsection{etherdoor} A very simple front-end based on React
using material styling; App's main \texttt{componentDidMount}
initializes the state including Web3 object and smart contract
wrapper, gets current connection status from backend's
\texttt{GET mac} endpoint and creates the micro-payment
state channel ephemeral account; at the end triggers a
\texttt{setInterval} loop that when connection activates,
will be responsible of sending proper signed micro-payments.

\begin{center}
  \includegraphics[keepaspectratio, width=0.4\textwidth]{images/portal-y.eps}
  \\
  Figure . \textit{etherdoor front-end landing page}
\end{center}

Usage depends on some button clicking, triggering
\texttt{someMinutesPass} function invokation that launches MetaMask
as Web3 provider making possible to the user to open a channel
on the smart contract building a transaction and relaying it
through \texttt{infuraProxy}; it also invokes \texttt{startChannel}
that will update React's App state and will cause
\texttt{signMicroPayment} function to periodically on a 10 seconds
interval to sign and post to the backend the increasing amount
micro-payments.

@@

To validate the PoC, a battery of tests has
been defined. For example, given
that smart contract normally handle money,
it is essential to ensure that
its number of failures and vulnerabilities is low [Hegedus 18].

\subsection{State channel contract tests}

During development and in order to ease
the automatic deployment of the contract
over a Truffle's suite Ganache-CLI\ref{ganache}
instance there are two util scripts on the
repository\cite{state-channel-contract-a}
\texttt{utils/compile.js} and \texttt{utils/deploy.js}
that take care of merging all the Solidity source
code required and deploying it to the Ganache instance.

In repository\cite{state-channel-contract-a} module
\texttt{tests/main.test.js} there are the following Mocha
framework\cite{mocha} based tests; tests use Chai assertion
library\cite{chai} using its \textit{should} mode whenever
possible but some of the assertions still have to be done
by \texttt{try-catch} pattern due to Chai not supporting
at the time of writing \texttt{BigInt} operation.

To help developers and make technology more mature,
we need analysis tools [ConsenSys 19].

@@

\bibitem{ganache}
  \href{https://github.com/trufflesuite/ganache-cli}{https://github.com/trufflesuite/ganache-cli}

\bibitem{express}
  \href{https://expressjs.com/}{https://expressjs.com/}
\bibitem{mocha}
  \href{https://mochajs.org/}{https://mochajs.org/}
\bibitem{chai}
  \href{https://chaijs.org/}{https://chaijs.org/}
